### 2014-06-12 ApTranscriptome_TR.Rmd
Rolled back RxNtype function to only High, Low, Bimodal and Intermediate categories output

**June 2, 2014**

@@

# Load libraries
library(R.utils)
library(ggplot2)
library(knitr)
library(knitcitations)
library(pander)
library(stringr)
library(data.table)
library(RCurl)
library(plyr)
library(MASS)
library(xtable)
library(methods) # required by `knitcitations` when file is `knit` from command-line
library(reshape2)

@@

# plot
mosaicplot(t(tt2), ylab = "AcNC", xlab = "ApVT", main = "Mosaic plot of responsive transcripts")
```

>>>>

**June 12, 2014**

@@

# Load libraries
library(R.utils)
library(ggplot2)
library(knitr)
library(knitcitations)
library(pander)
library(stringr)
library(data.table)
library(RCurl)
library(plyr)
library(MASS)
library(xtable)
library(methods) # required by `knitcitations` when file is `knit` from command-line
library(reshape2)
library(RColorBrewer)

@@

# plot
mosaic.colors <- brewer.pal(5, "Blues")

par(mar = c(5.1, 4.1, 4.1, 5.1))
mosaicplot(tt2, ylab = "A. picea", xlab = "", main = "", color = mosaic.colors, cex.axis = 0.01)
labels <- c("High", "Low", "Bimodal", "Intermediate", "NotResp")
text(c(.1,.3,.55,.75,.95), par("usr")[3] - 0.05, srt = 45, adj = 1, labels = labels, xpd = TRUE)
text(par("usr")[2] + 0.25, c(.95, .75, .55, .35, .1), srt = 0, adj = 1, labels = labels, xpd = TRUE)
text(.5, par("usr")[4] + .1, "A. carolinensis", xpd = TRUE)
```
